\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Bhautik Vaidya}

\section{Work experience}

\begin{eventlist}

\item{Feb 2011 -- PRESENT}
     {ZADCO, Abu Dhabi, UAE}
     {PMC Project Engineer and PMC Lead Instrumentation Engineer}

Worked on multiple projects ranging from water treatment to switch gear replacement. I was responsible for negotiating with and supporting contractors and resolving issues ranging from procurement of instruments to safety. **Note***

\item{Jul 2007 -- Feb 2011}
     {Hyundai Heavy Industries, Ulsan, S. Korea}
     {Lead Control and Instrumentation Engineer}

I led detail engineering, made purchase and change orders and carried out Control & Instrumentation engineering. I ensured high safety and security standards for the clients and overlooked the designing and construction of many instruments relating to fuel processing. I also claimed successful Change Orders for work done outside contractual obligations.

\item{Dec-2006 -- Jul-2007}
     {TECNIMONT ICB PVT. LTD.}
     {Senior Manager Control and Instrumentation}

I coordinated the design engineering and ensured correct specifications from the vendors. Additionally, I managed inspection activities with clients. 

\item{Mar-1998 -- Dec-2006}
     {
CERTIFICATION ENGINEERS INTERNATIONAL LTD.}
     {Principal Engineer}

I worked on multiple projects with different contractors in various countries (Sudan, S. Korea, etc.). With this company, I have worked on offshore platforms, refineries and cross country pipelines. In these projects, I have made feasibility reports, managed to expedite work flow significantly (the Sudanese government gave the team commendation) and ensured quality control as the client representative. 

\item{September 1996 -- September 1998}
     {Nuclear Power Corporation of India, LTD}
     {Scientific Assistant}

Coordinated the teams for the engineering, procurement, fabrication, installation and commissioning of 235MW nuclear power plants at multiple locations. I was in team that developed the first indigenous instruments for various uses in the power plants. Moreover, I was responsible for ensuring nuclear safety compliance in all the projects.  

\end{eventlist}

\personal
    [linkedin.com/in/bhautikvvaidya/]
    {1402, Sana Laundry Building, Khalifa St., \newline Abu Dhabi, UAE}
    {+971-55-163-4362}
    {bhautik.vaidya@gmail.com}
    
\section{Areas of Expertise}

\begin{itemize}
    \item Design management and Detailed eng.
    \item Preparing of Bids and Invitations to Tender
    \item Expediting, Inspecting and providing specialist support (debugging)
    \item Managing and preparing change orders.
    \item Making various Risk analysis like HAZID, etc.
    \item Development, Review and Approval of Technical Specifications and procedures
    \item Brownfield Project \& Shutdown job executions 
\end{itemize}
    


\section{Education}

\begin{yearlist}

\item[Sardar Patel CoE, Univ of Mumbai]{June 1992}
     {Electrical Engineering BE}
     {First Class (Honours); specialization: Control \& Instrumentation.}

\item[Bhagubhai M. Polytechnic]{August 1988}
     {Electrical Eng., Diploma}
     {First class and Distinction}

\end{yearlist}

\section{Professional Training, Memberships and Registrations}

\begin{factlist}
\item{}{Honeywell DCS EPKS and C300 Foundations}
\item{}{Chartered Engineer-Inst. of Engineers (India)}
\item{}{Lead Auditor-IRCA}
\item{}{Certified Quality Engineer -Indian Institute of Quality Management}
\end{factlist}


\section{Computer skills}

\begin{multiline}
   Smart Plant Instrumentation /INtools, INTRUCAL, AutoCAD2000, etc. 
\end{multiline}

\section{Professional skills}

\begin{multiline}
   Design Management, Bid preparation, Managing Emergency events, Safety Evaluations and specifications,  Risk Analysis, Managing Change Orders.
\end{multiline}

\end{document}
